---
title: "Creating a mp4 of satellite images"
author: "EE Holmes"
date: "8/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Creating mp4 of satellite images

This assumes that you already have all the images in a directory.

Load the packages.  
```{r load_packages}
library(ggplot2) # plotting
library(magick) # for image_* functions
```

## Step 1. Install FFmpeg if needed

Here is how to do it on a Mac (MacOS Sierra 10.12.6); Google to figure this out for Windows or Unix.

1. Open up utilities (in apps), and open Terminal.  
2. Type the following on the command line to install `brew`
```
ruby -e "$(curl -fsSL https://raw.github.com/mxcl/homebrew/go/install)"
```
3. Then you can install FFmpeg with this command.
```
brew install ffmpeg
```

## Make animation with animation and FFmpeg

```
library(animation)
fil_dir = "wheremypngsare"
imgs <- list.files(path=fil_dir,pattern="*.png", full.names = T)
saveVideo({
  for(img in imgs){
    im <- magick::image_read(img)
    plot(as.raster(im))
  }
},
video.name="myanimation.mp4"
)
```

The problem is that the mp4 is low quality.  You can change that but you need to dig into the documentation for FFmpeg.

## Alternative.  Use free gif to mp4 converter

Make a gif and then upload to [A free gif to mp4 converter]( https://ezgif.com/gif-to-mp4) like this one.

## More complicated example

I wanted to merge 4 images from 4 years and have a legend at the bottom.  Here's how I did it using ImageMagick to make a big gif (13M) and then uploaded that to ezgif.com to make a much smaller movie.

<div style="text-align:center" markdown="1">

<video width="400" controls>
  <source src="Kochin_SST_2014-17_4x4.mp4" type="video/mp4">
  Your browser does not support HTML5 video.
</video>

</div>

## The code

Here is the code I used
```{r make_4x4_movie}
# get the names of each file
imgs=list()
for(j in 1:4){
  year=as.character(2014:2017)[j]
  fil_dir <- paste0("india_sst_pngs_",year)
  imgs[[j]] = list.files(path = fil_dir, pattern = "*.png", full.names = T)
}

# Then make the gif
img = c()
imgleg = image_read("legend.png")
  for(i in 1:length(imgs[[1]])){
    theimgs=list()
    for(j in 1:4){
      theimgs[[j]]=image_read(imgs[[j]][i])
      theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 230, height = 332, x_off = 28, y_off = 0))
    }
    imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]]))
    imbot <- image_append(image_join(theimgs[[3]],theimgs[[4]]))
    im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
    img <- image_join(img, im)
  }
imggif = image_animate(img, fps=4, loop=1)
image_write(imggif, "Kochin_SST_2014-17_4x4.gif")
```

I could also do the same with animation

```{r animation_4x4_movie}
# you can use animation package but the default settings give a low quality movie
library(animation)
library(magick)
imgleg = image_read("legend.png")
saveVideo({
  for(i in 1:length(img14)){
    theimgs=list()
    for(j in 1:4){
      theimgs[[j]]=image_read(imgs[[j]][i])
      theimgs[[j]] = image_crop(theimgs[[j]], geometry_area(width = 230, height = 332, x_off = 28, y_off = 0))
    }
    imtop <- image_append(image_join(theimgs[[1]],theimgs[[2]]))
    imbot <- image_append(image_join(theimgs[[3]],theimgs[[4]]))
    im <- magick::image_append(image_join(imtop, imbot, imgleg), stack=TRUE)
    plot(as.raster(im))
  }
  },
video.name="Kochin_SST_2014-17.mp4"
)
```

